---
title: "DANL 200: Introduction to Data Analytics<br>Project"
subtitle: "Quarto Template<br><br>" 
author: 
  - name: Bailey
    affiliations:
      - SUNY Geneseo
  - name: Josh
    affiliations:
      - SUNY Geneseo
  - name: Marcus
    affiliations:
      - SUNY Geneseo
  - <br>
date: "`r Sys.Date()`"

format: 
  html:
    toc: true
    number-sections: true
    code-fold: false      
    code-summary: "Show the code"
    code-tools: true
    highlight-style: espresso # 

execute: 
  echo: true
  eval: true
  warning: false
  message: false
  fig-width: 9
---

```{r setup, include = FALSE}
library(tidyverse)

path <- 'https://bcdanl.github.io/data/climate_finance_energy.csv'
climate_finance <- read_csv(path)

library(skimr)

```

```{r}
BS <- read_csv('https://bcdanl.github.io/data/climate_finance_energy.csv')
nvars <- format(round(ncol(BS), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(BS), 0), 
                nsmall=0, 
                big.mark=",")
```

-   Here is the paged table using `rmarkdown::paged_table()`. Each country in the "party" category is the country that is providing the aid to the recipient country

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(BS) 
```

<br>

The number of variables is `r nvars`; the number of observations is `r nobs`.

<br>

# Introduction

This project is going to be used for our DANL 200 course. The primary reason our projet matters would be to showcase how over the semester we have learned how to code and this is the final "test" in a sense of what we have learned to do.The data set we choose to use for this project address relations between other countries and showcases which coutires provide aid to other countries. In this project, these questions will be coverd.

-which country provides the most support

-whih country providees the least support

-why this subject matters

-is there a coralation between where a country is and why it may contriburte more to other countries

-


# Data

## Data Summary

1.  **Party**

    -   Count: 3

    -   Unique Values: 2

2.  **Recipient Country/Region**

    -   Count: 3

    -   Unique Values: 2

3.  **Project/Program/Activity**

    -   Count: 1

    -   Unique Values: 1

4.  **Type of Support**

    -   Count: 3

    -   Unique Values: 1

5.  **Year**

    -   Count: 3

    -   Mean: 2015.67

    -   Standard Deviation: 1.15

    -   Min: 2015

    -   25th Percentile: 2015

    -   Median (50th Percentile): 2015

    -   75th Percentile: 2016

    -   Max: 2017

6.  **Contribution**

    -   Count: 3

    -   Mean: 13,495.39

    -   Standard Deviation: 3,209.92

    -   Min: 11,074.20

    -   25th Percentile: 11,674.88

    -   Median (50th Percentile): 12,275.56

    -   75th Percentile: 14,705.99

    -   Max: 17,136.41

7.  **Status**

    -   Count: 3

    -   Unique Values: 1

8.  **Energy**

    -   Count: 3

    -   Unique Values: 1

## Data Visualization

```{r}
ggplot(BS, aes(x = Contribution)) +
  geom_histogram(bins = 100,
                 fill = "blue", 
                 color = "black") +
  theme_minimal() +
  labs(title = "Histogram of Contributions",
       x = "Contribution",
       y = "Frequency")

 
```

## Data Transformation

```{r}
climate_finance_transformed <- climate_finance %>%
  mutate(
    Year = as.factor(Year),
    Contribution_Normalized = scales::rescale(Contribution, to = c(0, 1)),
    Energy_Encoded = as.numeric(Energy),
    Contribution_Category = cut(Contribution, 
                                breaks = c(-Inf, 10000, 50000, Inf), 
                                labels = c('Low', 'Medium', 'High')),
    Year_Group = ifelse(Year <= 2010, 'Before 2010', 
                        ifelse(Year <= 2015, '2011-2015', 'After 2015'))
  )

# View the transformed data
head(climate_finance_transformed)


```
 
<br><br><br><br>

# References

-   <https://quarto.org/docs/output-formats/html-basics.html>

-   <https://quarto.org/docs/websites/>

-   
